|

### 2020-05-17 paper/Manuscript.Rmd
manual change to resolve conflicts

author: #"`r source('authors_yaml.R')`"
  - name: "Caspar J. Van Lissa"
    institution: "1,2"
    orcid: "0000-0002-0808-5024"
    corresponding: yes
    address: "Padualaan 14, 3584CH Utrecht, The Netherlands"
    email: "c.j.vanlissa@uu.nl"
  - name: "Andreas M. Brandmaier"
    institution: "3,4"
    orcid: "0000-0001-8765-6982"
  - name: "Loek Brinkman"
    institution: "2,5"
    orcid: "0000-0003-3997-1173"
  - name: "Aaron Peikert"
    institution: "6"
    orcid: "0000-0001-7813-818X"
  - name: "Barbara M.I. Vreede"
    institution: "7"
    orcid: "0000-0002-5023-4601"

>>>>

author: #"`r source('authors_yaml.R')`"
  - name: "Caspar J. Van Lissa"
    institution: "1,2"
    orcid: "0000-0002-0808-5024"
    corresponding: yes
    address: "Padualaan 14, 3584CH Utrecht, The Netherlands"
    email: "c.j.vanlissa@uu.nl"
  - name: "Andreas M. Brandmaier"
    institution: "3,4"
    orcid: "0000-0001-8765-6982"
  - name: "Loek Brinkman"
    institution: "2,5"
    orcid: "0000-0003-3997-1173"
  - name: "Aaron Peikert"
    institution: "3,6"
    orcid: "0000-0001-7813-818X"
  - name: "Barbara M.I. Vreede"
    institution: "7"
    orcid: "0000-0002-5023-4601"
